Estimating migration rates for iteroparous species using kinship pairs found between populations\protect\thanks{Running head line: Estimating migration rates using kinship pairs}

### 2021-05-27 latex/ms.tex
change title and add text in Theory

\title{Estimating migrantation rates using kinship pairs \protect\thanks{Running head line: Estimating migrantation rates using kinship pairs}}

@@

\section{Theory}\label{sec2}
The main symbols used in the current paper are summarized in Table \ref{symbols}.

@@

\subsection{Hypothetical population and sampling scheme}

Suppose that we have a set of two populations labelled 1 and 2.

>>>>

\title{Estimating migration rates for iteroparous species using kinship pairs found between populations\protect\thanks{Running head line: Estimating migration rates using kinship pairs}}

@@

\section{Theory}\label{sec2}
In this section, we derivate the estimators of migrant number and migration rates using HS pairs or PO pairs found between two populations. While the estimators can hold under complex assumptions for reproduction theoretical foundation for estimating
このセクションでは、migrantやmigration rateの推定量を導出する。導出された推定量は、付録にある通りフレキシブルな仮定のもとでも成立するが、ここではシンプルな状況を例に出して説明する。The main symbols used in the current paper are summarized in Table \ref{symbols}.

@@

\subsection{Hypothetical population}

Suppose that we have a set of two populations labelled 1 and 2. Mating occurs within each population and parents can move to the other population after the end of the reproductive season. Hereafter, without loss of generality, we consider the parents that move from population 1 to population 2. In this study, a mature individual is called a parent even if it does not produce offspring.

ある年に集団１ではN1のおやがいるとする。親とは〜。交配はN1の集団内だけで行われ、産卵シーズン終了後に一部の親が集団２に移動する。翌年に、集団２ではN2個体の親がいて、そのうちの一部は集団１から移動してきた親であるとする。移動親のうち、集団２における産卵期まで生存した数をMとする。

\subsection{Sampling}
